Transferability of clinical prediction models for early trauma care

### 2019-08-18 ManuscriptMarkdown.Rmd
Update ManuscriptMarkdown.Rmd

## LOAD FUNCTIONS, ENVIROMENT AND TABLES
  ## Source functions
  source("functions/WorkTableCreator.R")
  ## Retrive original results
  results <- readRDS("output/original.results.Rds")
  ## Retrive data frame with compiled results
  result.tables.data.frame <- readRDS("result.tables.data.frame.Rds")
  ## Create table from result.tables.data.frame for ease of data retrival in document
  results.all.data <- WorkTableCreator(result.tables.data.frame)

## RESULTS
  ## Total patients and NA
  total.number.of.patients <- nrow(results$data.sets.before.imputations$multi.centre.vs.single.centre$multi.centre)
  total.number.of.na <- results$NA.info.sample$multi.centre.vs.single.centre$multi.centre$total.number.of.na
  ## Sample NA
  na.vector <- unlist(results$NA.info.sample)
  names(na.vector) <- c("high volume", "high volume", "low volume", "low volume", "metropolitan", "metropolitan", "non metropolitan", "non metropolitan", "multi centre", "multi centre", "single centre", "single centre")
  highest.percent.missing.number <- max(na.vector[na.vector<100])
  highest.percent.missing.name <- names((na.vector[na.vector == highest.percent.missing.number]))
  ## Variable NA
  number.variable.na <- max(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na)
  percent.variable.na <- results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$percentage[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na]
  name.variable.na <- row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na,])
  gcs.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_gcs_sum",])
  sbp.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_sbp_value",])
  ## Development and validation
  ## Imputation data
  high.low.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "high.volume"]
  metro.non.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "metropolitan"]
  multi.single.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "multi.centre"]
  max.imp <- max(results$original.stats$Total.imputations)
  ## Validation data
  sorted.validation.mistriage <- sort(results.all.data[row.names(results.all.data) == "Validation.mistriage",], decreasing = FALSE)
  lowest.val.mistriage <- sorted.validation.mistriage[1]
  val.undertriage <- results.all.data["Validation.undertriage", colnames(lowest.val.mistriage)]
  val.overtriage <- results.all.data["Validation.overtriage", colnames(lowest.val.mistriage)]
  highest.val.mistriage <- sorted.validation.mistriage[6]
  ## Comparison
  ## Transfer data
  sorted.transfer.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transfer.mistriage",], decreasing = FALSE)
  lowest.tran.mistriage <- sorted.transfer.mistriage[1]
  highest.tran.mistriage <- sorted.transfer.mistriage[6]
  ## Comparison data
  sorted.comp.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transferred.mistriage.minus.buddy.local.mistriage",], decreasing = FALSE)
  highest.comp.mistriage <- sorted.comp.mistriage[6]
  worst.transfer <- results$original.stats[results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median == max(results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median),]

@@

## Comparison
Model performance after transfer was determined for each model after being transferred
to the other sample in the data set in all data sets (Table 3). When
transferred, the model with the lowest mistriage rate was the `r colnames(lowest.tran.mistriage)` 
model, with a median mistriage rate of `r lowest.tran.mistriage`. The model with 
the highest mistriage rate after transfer was the `r colnames(highest.tran.mistriage)` model 
with a median mistriage rate of `r highest.tran.mistriage`.

>>>>

## LOAD FUNCTIONS, ENVIROMENT AND TABLES
  ## Source functions
  source("functions/WorkTableCreator.R")
  ## Retrive original results
  results <- readRDS("output/original.results.Rds")
  ## Retrive data frame with compiled results
  result.tables.data.frame <- readRDS("result.tables.data.frame.Rds")
  ## Create table from result.tables.data.frame for ease of data retrival in document
  results.all.data <- WorkTableCreator(result.tables.data.frame)
  ## Set names in in retrival table for correct formatting
  names(results.all.data) <- c("high-volume", "low-volume", "metropolitan", "non-metropolitan", "multiple centres", "single centre")

## RESULTS
  ## Total patients and NA
  total.number.of.patients <- nrow(results$data.sets.before.imputations$multi.centre.vs.single.centre$multi.centre)
  total.number.of.na <- results$NA.info.sample$multi.centre.vs.single.centre$multi.centre$total.number.of.na
  ## Sample NA
  na.vector <- unlist(results$NA.info.sample)
  names(na.vector) <- c("high-volume", "high-volume", "low-volume", "low-volume", "metropolitan", "metropolitan", "non-metropolitan", "non-metropolitan", "multiple centres", "multiple centres", "single centre", "single centre")
  highest.percent.missing.number <- max(na.vector[na.vector<100])
  highest.percent.missing.name <- names((na.vector[na.vector == highest.percent.missing.number]))
  ## Variable NA
  number.variable.na <- max(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na)
  percent.variable.na <- results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$percentage[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na]
  name.variable.na <- row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na,])
  gcs.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_gcs_sum",])
  sbp.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_sbp_value",])
  ## Development and validation
  ## Imputation data
  high.low.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "high.volume"]
  metro.non.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "metropolitan"]
  multi.single.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "multi.centre"]
  max.imp <- max(results$original.stats$Total.imputations)
  ## Validation data
  sorted.validation.mistriage <- sort(results.all.data[row.names(results.all.data) == "Validation.mistriage",], decreasing = FALSE)
  lowest.val.mistriage <- sorted.validation.mistriage[1]
  val.undertriage <- results.all.data["Validation.undertriage", colnames(lowest.val.mistriage)]
  val.overtriage <- results.all.data["Validation.overtriage", colnames(lowest.val.mistriage)]
  highest.val.mistriage <- sorted.validation.mistriage[6]
  ## Comparison
  ## Transfer data
  sorted.transfer.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transfer.mistriage",], decreasing = FALSE)
  lowest.tran.mistriage <- sorted.transfer.mistriage[1]
  highest.tran.mistriage <- sorted.transfer.mistriage[6]
  ## Comparison data
  sorted.comp.mistriage <- sort(results.all.data[row.names(results.all.data) == "Transferred.mistriage.minus.buddy.local.mistriage",], decreasing = FALSE)
  highest.comp.mistriage <- sorted.comp.mistriage[6]
  worst.transfer <- results$original.stats[results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median == max(results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median),]

@@

## Comparison
Model performance after transfer was determined for each model after being transferred
to the other sample in the data set, in all data sets (Table 3). When
transferred, the model with the lowest mistriage rate was the `r colnames(lowest.tran.mistriage)` 
model, with a median mistriage rate of `r lowest.tran.mistriage`. The model with 
the highest mistriage rate after transfer was the `r colnames(highest.tran.mistriage)` model 
with a median mistriage rate of `r highest.tran.mistriage`.
